---
title: "Project 1 Group Code"
author: "Ely, Kalen, Rayon"
date: "2/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Libraries
library("tidyverse")
library("ggplot2")
library("GGally")
library("naniar")

```




```{r}
# Read Data <- This will be different for each of us.

#Ely's read data line
#car_data = read.csv("~/Desktop/applied_stats/data1.csv")

# Rayon's read data line
car_data <-  read.csv("data1.csv")
attach(car_data)

```


# Cleaning Data

```{r}
# Change categorical attributes to factors

car_data$Make = as.factor(car_data$Make)
car_data$Model = as.factor(car_data$Model)
car_data$Engine.Fuel.Type = as.factor(car_data$Engine.Fuel.Type)
car_data$Transmission.Type = as.factor(car_data$Transmission.Type)
car_data$Driven_Wheels = as.factor(car_data$Driven_Wheels)
car_data$Vehicle.Size = as.factor(car_data$Vehicle.Size)
car_data$Market.Category = as.factor(car_data$Market.Category)
car_data$Vehicle.Style = as.factor(car_data$Vehicle.Style)


```

```{r}
# Evaluate if there is missing information - NA
gg_miss_var(car_data)

# Visualize the missing data.
vis_miss(new_AutoM)
```


```{r}


# Missing Doors

car_data %>%
  filter(is.na(Number.of.Doors))

# Other Tesla Model S 2016 have 4 doors - manual fix
car_data %>%
  filter(Make == 'Tesla' & Model == 'Model S' & Year == 2016)

car_data[(is.na(car_data$Number.of.Doors)&car_data$Make=='Tesla'),9] = 4

# There are no other 2013 FF Ferraris in our data set, but the other years have 2 doors, and some online research shows thee 2013 does as well - manual fix
car_data %>%
  filter(Make == 'Ferrari' & Model =='FF')

car_data[(is.na(car_data$Number.of.Doors)&car_data$Make=='Ferrari'),9] = 2


```


```{r}

# Engine Cylinders

car_data %>%
  filter(is.na(Engine.Cylinders))


# Mazda RX Models - These have a rotary engine, so have 0 cylinders

car_data[(is.na(car_data$Engine.Cylinders) & car_data$Make == 'Mazda'),6]= 0

# Other missing cylinder cars are all electric

car_data[(is.na(car_data$Engine.Cylinders) & car_data$Engine.Fuel.Type == 'electric'),6]= 0


```

```{r}

# Engine Horsepower

car_data %>%
  filter(is.na(Engine.HP))

#  Using the base horsepower I can find online for these Some versions have higher horsepower, but this data set does not give us the attributes needed to identify these.

car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Model S' & Year == 2014),5] = 302
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Model S' & Year == 2015),5] = 329
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Model S' & Year == 2016),5] = 315
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='500e' & Year == 2015),5] = 111
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='500e' & Year == 2016),5] = 111
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='500e' & Year == 2017),5] = 111
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Continental' & Year == 2017),5] =305
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Escape' & Year == 2017),5] = 168
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Fit EV' & Year == 2013),5] = 123
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Fit EV' & Year == 2014),5] = 123
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Focus' & Year == 2015),5] = 123
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Focus' & Year == 2016),5] = 123
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Focus' & Year == 2017),5] = 123
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Freestar' & Year == 2005),5] = 193
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='i-MiEV' & Year == 2014),5] = 66
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Impala' & Year == 2015),5] = 195
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Impala' & Year == 2016),5] = 196
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Impala' & Year == 2017),5] = 197
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Leaf' & Year == 2014),5] = 107
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Leaf' & Year == 2015),5] = 107
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Leaf' & Year == 2016),5] = 107
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='M-Class' & Year == 2015),5] = 302
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='MKZ' & Year == 2017),5] = 240
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='RAV4 EV' & Year == 2013),5] = 154
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='RAV4 EV' & Year == 2014),5] = 154
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Soul EV' & Year == 2015),5] = 109
car_data[(is.na(car_data$Engine.HP) & car_data$Model=='Soul EV' & Year == 2016),5] = 109




# Double Check NA Values - Looks good!
gg_miss_var(car_data)
sapply(car_data, function(x) sum(is.na(x)))

```

```{r}
# Unnown Transmission Types

car_data %>%
  filter(Transmission.Type == 'UNKNOWN')

# Based off of other RAM 150s
car_data[(car_data$Transmission.Type == 'UNKNOWN' & car_data$Model=='RAM 150'),7] = 'MANUAL'

# Based off of online research
car_data[(car_data$Transmission.Type == 'UNKNOWN' & car_data$Model=='Achieva'),7] = 'AUTOMATIC'

# Other 3 models with unknown transmissions don't have enough identifiable info to fix, so we'll drop these 9 rows.

car_data = car_data %>%
  filter(Transmission.Type != 'UNKNOWN')

# Refactor transmission type to exclude UNKNOWN
car_data$Transmission.Type = as.character(car_data$Transmission.Type)
car_data$Transmission.Type = as.factor(car_data$Transmission.Type)


```

```{r}
summary(car_data)


```

```{r}


# Seeing odd values for max HP, Engine Cylinders,MPG, and MSRP

# HP and MSRP looks correct
car_data %>%
  filter(Engine.HP > 700)

# Cylinders looks correct based on car and HP
car_data %>%
  filter(Engine.Cylinders > 10)

# Highway MPG for this item is false - manual fix based on online research
car_data %>%
  filter(highway.MPG > 300)

car_data[car_data$highway.MPG == 354,13] = 32

# All high city mpgs are electric, as expected
car_data %>%
  filter(city.mpg > 100)


# N/A Strings in Market Category

# These N/A Values range over a wide variety of car types. We'll choose to keep these values in the data set unless we need to create a model using market category

head(
  car_data %>%
    filter(Market.Category == 'N/A')
    )
```







# Training / Test Split

```{r}
set.seed(1234)
index = sample(1:dim(car_data)[1],9525,replace=F)

train = car_data[index,]

test_validate = car_data[-index,]
test_index = sample(1:dim(test_validate)[1],1190,replace=F)

train = car_data[index,]
test = test_validate[test_index,]
validate = test_validate[-test_index,]

head(train)
head(test)
head(validate)
```


# EDA


```{r}

head(train)
pairs(train[,c(16,3,5,6,9,13,14,15)])

```


**Initial Findings**

  * City and highway mpg are highly correlated
 
  * Seeing some correlation between HP, Cylinders, and MPG as well
 
```{r}
pairs(train[,c(15,5,6,13,14)])
```

**Findings**
 
  * We'll need to choose between HP vs Cylinders and Highway mpg vs City mpg
 
```{r}
pairs(train[,c(16,5,6)])

pairs(train[,c(16,13,14)])

# highway mpg is statistically significant when used as a predictor for popularity while city mpg is not. We'll go with highway mpg
summary(lm(MSRP ~ highway.MPG, data = train))[4]
summary(lm(MSRP ~ city.mpg, data = train))[4]

# Both are statistically significant - next we'll test to see how they hold up when paired with highway mpg
summary(lm(MSRP ~ Engine.HP, data = train))[4]
summary(lm(MSRP ~ Engine.Cylinders, data = train))[4]

pairs(train[,c(16,5,6,13)])
summary(lm(Popularity ~ Engine.HP + highway.MPG, data = train))[4]
summary(lm(Popularity ~ Engine.Cylinders + highway.MPG, data = train))[4]

# Seeing some collinearity between mpg, horsepower, and cylinders. We'll move forward with caution using highway mpg and cylinders, understanding that we may ultimately need to decide between the two.

head(train)

#Numerical
pairs(train[,c(16,6,9,13,15)])

#Seeing some correlation with MSRP vs Fuel Type and MSRP vs Make, and MSRP vs Year
pairs(train[,c(16,1,3,4)])

pairs(train[,c(16,7:11)])
```
## Importance of Popularity:

#### Popularity is broken down by make - not by model. Also, no two makes have the same popularity. This means that popularity has a 1-1 relationship with Make, so we only need one of them

```{r}
car_data %>%
  select(Make, Model, Popularity) %>%
  group_by(Make) %>%
  summarize(count = n(), max = max(Popularity), min = min(Popularity)) %>%
  arrange(max)
```

#### Popularity vs MSRP

```{r}

# Seeing a slight negative trend between popularity score and MSRP
train %>%
  ggplot(aes(x = Popularity, y = MSRP)) +
  geom_point() +
  geom_smooth(method = 'lm', color = 'red')

summary(lm(MSRP~Popularity, data = train))
```

<br>

**Findings**

  * There exists a negative correlation between popularity score and MSRP
   
    * This may indicate that more affordable cars are more popular
   
  * The relationship between popularity and MRSP is statistically significant